# Introduction

```{r , include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

# clear environment
rm(list=ls())

# load packages
library(bookdown)
library(tinytex)
library(tidyverse)
library(googlesheets4)
library(lubridate)
library(readr)
library(readxl)
library(writexl)
library(hms)
library(plotly)
library(DT)
library(xlsx)
library(leaflet)
library(DT)
library(ggpubr)
library(plotrix)
library(packrat)
library(foreign)

# set plotting themes

## geom_col plots theme
col_theme <- theme(axis.title = element_text(size = 14, face = "bold"),
                   strip.text = element_text(size = 14, face = "bold"),
                   legend.title = element_text(size = 14, face = "bold"),
                   legend.text = element_text(size = 14),
                   axis.text = element_text(size = 14))

## geom_points plots theme
points_theme <- theme(axis.title = element_text(size = 14, face = "bold"),
                   strip.text = element_text(size = 14, face = "bold"),
                   legend.title = element_text(size = 14, face = "bold"),
                   legend.text = element_text(size = 14),
                   axis.text = element_text(size = 11, face = "bold"),
                   title = element_text(size = 18))

# function to exclude multiple items per column
'%ni%' <- Negate('%in%')

# clarify select function
select <- dplyr::select
```

The following chapters contain data and analysis related to the Kenai River Thermal Imagery project conducted from 2020 - 2022. This work is a collaborative effort between three Kenai Peninsula Nonprofits: Cook Inletkeeper, Kachemak Bay Heritage Land Trust, and Kenai Watershed Forum. It is funded by the Alaska Sustainable Salmon Fund (project #53003).

```{r echo = F}

xfun::embed_file("documents/AKSSF Thermal Imagery SOW.docx", text = "Download the Project Scope of Work Document")

```

<br>

This report is generated using Quarto, an open source publishing platform. It is best accessed online at the url <https://kenai-watershed-forum.github.io/kenai_thermal_imagery_v2/>.

```{r echo = F, eval = F}

# The contents of this report can also be downloaded as an Microsoft Word document here:

xfun::embed_file("_book/Kenai-Thermal-Imagery_draft.docx", text = "Download This Report as a Microsoft Word Document")

```

<br>

All code used to generate this report is available in the project's GitHub repository at <https://github.com/Kenai-Watershed-Forum/kenai_thermal_imagery_v2>.
