# Introduction

```{r , include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

# clear environment
rm(list=ls())

# load packages
library(bookdown)
library(tinytex)
library(tidyverse)
library(googlesheets4)
library(lubridate)
library(readr)
library(readxl)
library(writexl)
library(hms)
library(plotly)
library(DT)
library(xlsx)
library(leaflet)
library(DT)
library(ggpubr)
library(plotrix)
library(packrat)
library(foreign)

# set plotting themes

## geom_col plots theme
col_theme <- theme(axis.title = element_text(size = 14, face = "bold"),
                   strip.text = element_text(size = 14, face = "bold"),
                   legend.title = element_text(size = 14, face = "bold"),
                   legend.text = element_text(size = 14),
                   axis.text = element_text(size = 14))

## geom_points plots theme
points_theme <- theme(axis.title = element_text(size = 14, face = "bold"),
                   strip.text = element_text(size = 14, face = "bold"),
                   legend.title = element_text(size = 14, face = "bold"),
                   legend.text = element_text(size = 14),
                   axis.text = element_text(size = 11, face = "bold"),
                   title = element_text(size = 18))

# function to exclude multiple items per column
'%ni%' <- Negate('%in%')

# clarify select function
select <- dplyr::select
```

The following chapters contain data and analysis related to the project conducted 2020 - 2022, "Kenai Mountains to Sea: Using Thermal Infrared Imagery to Implement Long-Term Salmon Conservation." This work is a collaborative effort between three Kenai Peninsula Nonprofits: Cook Inletkeeper, Kachemak Heritage Land Trust, and Kenai Watershed Forum. The project Scope of Work document may be downloaded at the link below:

```{r echo = F}

xfun::embed_file("documents/AKSSF Thermal Imagery SOW.docx", text = "Download the Project Scope of Work Document")

```

<br>

This report is generated in [Posit](https://posit.co/) (formerly known as RStudio) using the R programming language [@rcoreteam] and [Quarto](https://quarto.org/), an open source technical publishing platform. It is best accessed online at the url <https://kenai-watershed-forum.github.io/kenai_thermal_imagery_v2/>. 

## Access the PDF
This report can be downloaded as a PDF document by clicking on the PDF symbol in the upper left corner of this screen.

## Access Source Code
Source code used to generate this report is available in the project's GitHub repository, available by clicking the feline symbol in the upper left corner of this screen.



\newpage
